\documentclass[12pt,letterpaper]{article}
\usepackage{latexsym}
% \usepackage{times}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{lastpage}
\usepackage[hidelinks]{hyperref}

\usepackage[letterpaper,left=0.5in,top=0.5in,right=0.5in,bottom=0.5in,includehead]{geometry}

\hypersetup{
	pdfauthor={Mark Keele},
	pdftitle={Resume},
}

\fancyhf{}
\headwidth 7.5in
\setlength{\headheight}{22.67781pt}
\lhead{{\Huge \textbf{Mark Keele}}}
\rhead{\large \href{https://keele.codes}{https://keele.codes} -- \
\href{mailto:mark@keele.codes}{mark@keele.codes} -- \
(931) 434-9560}

\author{Mark Keele}
\title{Resume}
\date{\today}
\begin{document}

Web application developer with five years of experience. Extensive knowledge in operating systems, computer networks, and secure computing. Comfortable actualizing projects from conception to deployment. Ability to communicate with clients and derive requirements.

\noindent\rule{7.5in}{0.4pt}

\subsection*{Education}

\textbf{Master of Science in Computer Science -- May 2016} \\
% \hfill{GPA: 3.0/4.0} \\
\bigskip School of Informatics and Computing, Indiana University -- Bloomington, Indiana \\
\noindent\textbf{Bachelor of Science in Computer Science -- Dec. 2012} \\
% \hfill{GPA: 3.0/4.0}\\
College of Basic and Applied Sciences, Middle Tennessee State University -- Murfreesboro, Tennessee

\noindent\rule{7.5in}{0.4pt}

\subsection*{Work Experience}

\textbf{Research Assistant - Center for Research in Extreme Scale Technologies}
\hfill{08/2013 -- 05/2015} \\
Indiana University -- Bloomington, Indiana

\begin{itemize}

  % \item Developed and deployed both a client side and server side web
  % application that is used as a part of the GENI Network test bed.

  \item Developed and deployed an asynchronous client/server application
  built on top of web sockets. Gave users the ability to inspect nodes
  on the network, submit network performance tests, and visualize the results.

  % \item Exists as a layer in an existing network instrumentation and
  % measurement system. Communicates with a central application that represents
  % network topologies.

  \item Integrated as a layer in an existing network instrumentation and
  measurement system. Application added topological visualizations and
  facilitated the tracking of node performance data.

  % \item Presented conference talk on the functionality and capabilities of the software.
  % Made available for attendees to experiment with.

\end{itemize}


\noindent\textbf{Intern - Ruby on Rails Developer, Leadership Computing Facility}
\hfill{06/2012 -- 07/2013} \\
Oak Ridge National Laboratory -- Oak Ridge, Tennessee

\begin{itemize}

	\item Designed, developed, tested, and deployed a web application using the Ruby
	on Rails framework. Exposed to all layers of the modern web application stack.
  Application used internally to track resources and allocations
  of users and projects for the Supercomputers.

  \item Closely collaborated with mentor, database designer, system administrator,
  and key end users. Struck a balance between technical requirements and end user workflow.
  Continuous refactoring and regression testing were staple methodologies.

  % \item Engaged in Test Driven Development methodologies in a pair-programming environment
  % with an emphasis on continuous refactoring.
  % Regression testing using both scenario tests with Cucumber and unit tests with RSpec.

\end{itemize}


%\item \textbf{Lab Assistant, Business and Aerospace Lab}
%\hfill{05/2008 -- 05/2012} \\
%Middle Tennessee State University -- Murfreesboro, Tennessee
%
%\begin{itemize}
%
%  \item Assisted a high volume of students and faculty at the most visited
%  computer laboratory on campus.
%
%  \item Mastered all computer software and hardware available in the laboratory.
%  Software included Office Suite, Visual Studio, and AutoCAD. Hardware included
%  printers, scanners, projectors, touchscreens, and computers.
%
%\end{itemize}

%\item \textbf{Work Student Student, Computer Science Department}
%\hfill{08/2007 -- 05/2008} \\
%Middle Tennessee State University -- Murfreesboro, Tennessee

%\begin{itemize}

%	\item ...

%	\item ...

%\end{itemize}

%\pagebreak

%\item \textbf{Camera Operator, Peahead Productions}
%\hfill{08/2003 -- 08/2007} \\
%Channel 6 Studio -- Tullahoma, Tennessee

%\begin{itemize}

%	\item ...

%	\item ...

%\end{itemize}


% \subsection*{Course Projects}

% \begin{itemize}
%   \item \textbf{XINU OS on Raspberry Pi}
%   \begin{itemize}

%     \item Wrote basic operating system commands and added synchronization support using semaphores.

%     \item Included notion of futures and promises so that processes could synchronize on a given computation.

%   \end{itemize}

%   \item \textbf{Lux Ex Machina}
%   \begin{itemize}

%     \item An embedded system acting as a light meter that recommends shutter speed,
%     aperture, and ISO to the user. Accomplished using ARM board, light sensor, and
%     Wi-Fi adapter.

%     \item Front-end web application used to receive data, make calculations, and
%     respond to device dimensions. Experience was tailored for iPhone and Android smartphones.

%   \end{itemize}

% \end{itemize}

\noindent\rule{7.5in}{0.4pt}

\subsection*{Technical Skills}

\begin{itemize}

  \item\textbf{Programming Languages}: Ruby, JavaScript, and C/C++
  \item\textbf{Web Development}: Ruby on Rails, NodeJS, AngularJS, Nginx, JSON, and HTML
  \item\textbf{Databases}: MySQL, PostgreSQL, and MongoDB
  \item\textbf{Operating System}: Server Admin, Performance Monitoring, and System Calls
  \item\textbf{Networking}: Packet Routing, TCP/IP, HTTP/S, and RESTful Web Services
  \item\textbf{Security}: Access Control, Process Isolation, Public-Key Infrastructure, and Buffer Overflow
  \item\textbf{Methodologies}: Git, Agile, Test-Driven Development, and Regression Testing

\end{itemize}

\end{document}
