\documentclass[10pt,letterpaper]{article}
\usepackage{latexsym}
%\usepackage{times}
\usepackage{fancyhdr}
\pagestyle{fancy}
%\pagestyle{empty}
%\usepackage{lastpage}

\usepackage[letterpaper,left=0.75in,top=0.75in,right=0.75in,bottom=0.75in,includehead]{geometry}

\usepackage{hyperref}
\hypersetup{
	pdfauthor={Mark Keele},
	pdftitle={Resume},
}

\fancyhf{}
\headwidth 7.0truein
\lhead{{\Large \textbf{Mark Keele}} \\
%\lhead{{\Large Mark Keele} \\
%305 E 1st St. Bloomington, Indiana 47401  --  \
Phone: (931) 434-9560  --  E-mail: m.keele88@gmail.com}
%\rfoot{\thepage\ of \pageref{LastPage}}

\author{Mark Keele}
\title{Resume}
\date{\today}
\begin{document}

%\subsection*{Contact Information}
%\label{sub:contact_information}
%Address: 305 E 1st St. Bloomington, Indiana 47401  --  \
%Phone: (931) 434-9560  --  E-mail: m.keele88@gmail.com}
%% subsection contact_information (end)

%\subsection*{Objective}
%To secure an internship position for the Summer of 2015 with a concenration
%in Web Development, Networking, and Security where I can continue to
%work towards my goal of being proficient in the full stack of Web Development.

\subsection*{Education}

\begin{itemize}
	\item \textbf{Masters of Science in Computer Science -- In progress}
	\hfill{GPA: 4.00} \\
	School of Informatics and Computing, Indiana University -- Bloomington, Indiana
	\hfill{15 credit hours completed}

%	Conference talk on Network Instrumentation and Measurement. \\
%	Key Courses: Web Development, Advanced Operating Systems,
%	Embedded System Engineering, and Applied Networking

	\item \textbf{Bachelor of Science in Computer Science -- Completed 12/2012}
	\hfill{GPA: 3.20 }\\
	Basic and Applied Sciences, Middle Tennessee State University -- Murfreesboro, Tennessee
	\hfill{141 credit hours completed}
	%\\ Financed education with scholorships and living expenses working 20 hours per week as a Lab Assistant
\end{itemize}

\subsection*{Technical Skills}

\begin{itemize}

	%add job skills from description here

	\item Parallel application development in C and Fortran using MPI and
	OpenMP. Cloud application development using Java and the Apache Hadoop
	project. Additional Languages: Ruby, Python, and C++.

	\item Web application development with Ruby on Rails, JavaScript, CSS, and
	SQL including production level deployment with Linux, Apache, nginx,
	MySQL, PostgreSQL, Subversion, and Git.

  \item Comfortable with clustered Linux systems including shell scripting, the
  Torque resource manager, the Moab scheduler, and InfiniBand networking.

	%Additionally, Ruby on Rails application integration with Drupal, Flash,
	%and ASURITE (Arizona State University's campus wide single sign-on
	%service).

	%\item Accustomed to collaborative development with version control tools
	%such as Subversion and Git.

\end{itemize}


\subsection*{Work Experience}

\begin{itemize}

\item \textbf{Technical Support Analyst Senior, High Performance Computing Initiative}
%\hfill{February 2006 -- Present} \\
\hfill{06/2010 -- Present} \\
Arizona State University -- Tempe, Arizona

\begin{itemize}

	\item Administered the Saguaro High Performance Computing (HPC) system
	which ranked 160 in the Top 500 Supercomputer Sites as of June 2009.

	%Duties include: assisting with system wide upgrades, application and
	%library compilation/installation/testing, updating documentation, and
	%providing user support.

  \item Communicated with end users to provide application configuration,
  installation, testing, and deployment.

  \item Developed and delivered instructional short courses on parallel
  programming using the Message Passing Interface (MPI) on the Saguaro HPC
  system.

  \item Supported the day to day operations using technologies such as: Moab,
  Torque, the Gold Allocation System, Request Tracker, CFEngine, System Imager,
  FlexLM, and building custom RPMs from source installs.

  \item Interfaced with software and hardware vendors for upgrades and
  maintenance.

\end{itemize}


\item \textbf{Web Application Developer, Integrum Technologies LLC}
\hfill{01/2010 -- 06/2010} \\
260 South Arizona Avenue -- Chandler, Arizona
%\hfill{(6 months, 40 hrs/week)}

\begin{itemize}

	\item Designed, developed, and tested web applications using the Ruby
	on Rails framework.

	\item Worked directly with clients daily using SCRUM and Agile
	techniques to ensure a high amount of communication, fast turn around
	times, and thoroughly tested code.

  \item Performed a heavy amount of integration testing using Cucumber.

  \item Followed Test Driven Development methodologies in a pair-programming
  environment with an emphasis on continuous refactoring.

  \item Deployed production applications using technologies such as: MySQL,
  PostgreSQL, NGINX, Apache, Postfix, and Phusion Passenger.

\end{itemize}


\item \textbf{Research Assistant, High Performance Computing Initiative}
%\hfill{February 2006 -- Present} \\
\hfill{2/2006 -- 4/2008, 8/2008 -- 12/2009} \\
Arizona State University -- Tempe, Arizona
%\hfill{(44 Months, 20 hrs/week)}

\begin{itemize}

  \item Designed and built GDBase, an off-line framework for debugging MPI
  applications. It provides a method for users to define debugger behavior,
  collect results to a database, and analyze the information postmortem.

	%GDBase has been tested and deployed on the Saguaro system.

	%GDBase uses the GNU Debugger to capture debugging events across
	%Message Passing Interface (MPI) tasks and log them to a relational
	%database for postmortem analysis. Future work involves adding
	%performance data collection through the integration of profiling tools
	%with GDBase.

  \item Assisted Saguaro users with MPI application development, debugging,
  profiling, and error diagnosis.

  \item Trained users in MPI introduction short courses that covered data
  decomposition, MPI data types, check-pointing with MPI/IO, and debugging using
  the GNU Debugger (GDB) and GDBase.

  \item Streamlined error detection on Saguaro using a set of scripts to control
  job scheduling. If errors are found on a machine, staff members are notified,
  and jobs are then rescheduled to error free machines with no intervention.

  \item Developed ASULinx, a prototype Ruby on Rails social networking tool
  designed to highlight interdisciplinary relationships and collaborative
  research in a graphical manner.
	(\href{http://asulinx.asu.edu}{asulinx.asu.edu})

	%\item Researched and evaluated alternative parallel programming
	%paradigms for possible use on our cluster. Languages include: Unified
	%Parallel C, Co-Array Fortran, Shared Memory Programming Library, and
	%Charm++ among others.

\end{itemize}

%Supervisor: Dan Stanzione
%Engineering Research Center
%551 E Tyler St, ERC 552
%Tempe, AZ 85287
%(480) 727-8738
%
%Hours: 20/week
%Salary: \$16.85/hr

\item \textbf{Subject Matter Expert, Lionbridge Technologies}
\hfill{7/2009} \\
Microsoft -- Redmond, Washington
%\hfill{(1 week, 40 hrs/week)}

\begin{itemize}

	\item Authored and revised questions for the Microsoft HPC 2008
	certification exam.

\end{itemize}

\item \textbf{Web Developer, Office of the Vice President for Global Engagement}
\hfill{7/2008 -- 11/2008} \\
Arizona State University -- Tempe, Arizona
%\hfill{(5 Months, 20 hrs/week)}

\begin{itemize}

	\item Updated ASULinx to fit the needs of the Global Engagement Department.
	%(\href{http://ovpge.asu.edu/GlobaLinx}{ovpge.asu.edu/GlobaLinx})

	\item Collaborated with \href{http://www.esserdesign.com/}{Esser
	Design} on integrating new artwork.

\end{itemize}

%\pagebreak

\item \textbf{Graduate Student Intern, HPC-3 Department}
\hfill{5/2008 -- 7/2008} \\
Los Alamos National Laboratory (LANL) -- Los Alamos, New Mexico
%\hfill{(3 Months, 40 hrs/week)}

\begin{itemize}

	\item Worked towards porting the Stack Trace Analysis Tool (STAT) for
	use on the high performance computing (HPC) systems at LANL.
	%This tool allows researchers to debug their parallel code for use on
	%the HPC systems at Los Alamos National Laboratory.

	\item Collaborated with developers at Los Alamos National Laboratory
	and Lawrence Livermore National Laboratory on the Development of STAT.

\end{itemize}

%Supervisor: David Montoya
%Carol Hogsett - Recruiter/Student Liaison
%DCS, NIE, and HPC Divisions
%Los Alamos National Laboratory
%PO Box 1663, MS B260
%Los Alamos, NM  87545
%(VM) 505-665-4732
%FAX 505-665-4361
%
%Hours: 40/week
%Salary: \$23.67/hr


%\item \textbf{Student Worker (Technology Support), Physics and Astronomy}
%\hfill{11/2004 -- 1/2006}\\
%Arizona State University -- Tempe, Arizona
%%\hfill{(15 Months, 20 hrs/week)}

%\begin{itemize}

	%\item Solved technical problems with friendly service over the phone,
	%email, and in person.

	%\item Setup and maintained class laboratories with Linux, Mac OS X, and
	%Windows workstations.

	%\item Configured workstations and servers department wide for file and
	%printer sharing.

	%\item Managed a ticketing system to track support requests.

%\end{itemize}

%\item \textbf{Student Worker (Technology Support), Herberger College of Fine Arts}
%\hfill{6/2004 -- 10/2004}\\
%Arizona State University -- Tempe, Arizona
%\hfill{(5 Months, 20 hrs/week)}

%\begin{itemize}

	%\item Provided technical support to the schools of Architecture, Art,
	%Design, Music, and Theatre.

	%\item Diagnosed hardware and software problems on Mac and Windows
	%workstations.

	%\item Maintained systems though hardware and software upgrades.

%\end{itemize}

\end{itemize}


\subsection*{Publications}

\begin{itemize}

	\item ``Architecture for an Offline Parallel Debugger'' \\
	IEEE International Symposium on Parallel and Distributed Processing
	with Applications (ISPA), 12/2008.

	%http://portal.acm.org/citation.cfm?id=1494192

	\item ``A Scalable Framework for Offline Parallel Debugging'' \\
	9th Linux Cluster Institute (LCI) International Conference on
	High-Performance Clustered Computing, 4/2008.

\end{itemize}


% \subsection*{Coursework}
%
% \begin{itemize}
%
% \item \textbf{MPI Application Development} \\ A class covering
% methodologies for development of Message Passing Interface (MPI)
% applications with projects focusing on communication patterns, parallel
% input and output (MPI/IO), check pointing, and MPI/Open Multi-Processing
% (OpenMP) hybrid applications.
%
% \item \textbf{Cloud Computing} \\ Gained an understanding of distributed
% computing concepts and cloud computing architectures. Projects included
% developing distributed applications that use the Map/Reduce framework and
% Hadoop to solve large scale computing problems.
%
% \item \textbf{Applied Cryptography} \\ Application of cryptography
% technologies including SSL, RSA, and DES among other symmetric and
% asymmetric encryption schemes.
%
% \item \textbf{Software Security} \\ Class covering theories and tools for
% software security including secure design, threat analysis and modeling,
% security testing and coding. A course project involved creating a secure
% web application written in Ruby on Rails to manage documents for a company.
%
% \item \textbf{Relational Databases} \\ Database design and query
% techniques, studies included information retrieval from Oracle databases
% using Structured Query Language (SQL) queries.
%
% \item \textbf{Distributed Computing} \\ Project oriented course focusing on
% team development of web applications using Active Server Pages (ASP.NET)
% and standardized web services using Web Services Description Language
% (WSDL) in conjunction with Simple Object Access Protocol (SOAP).
%
% \end{itemize}

%\subsection*{References}
%
%\begin{itemize}
%
%\item \textbf{Doug Fuller} \\
%Computational Scientist, Oak Ridge National Laboratory \\
%Phone: (865) 241-2850 -- Email: fullerdj@ornl.gov
%
%\item \textbf{Kirt Karl} \\
%Systems Engineer, Isilon Systems \\
%Phone: (480) (480) 559-3032 -- Email: kirt.karl@isilon.com
%
%\item \textbf{Christopher Young} \\
%Ruby on Rails Software Developer and Scrum Master, Equipco, LLC \\
%Phone: (602) 577-4832 -- Email: chris@equiprent.com
%
%%\item \textbf{Gil Speyer} \\
%%Research Scientist, Fulton High Performance Computing Initiative, Arizona
%%State University \\
%%Phone: (480) 727-8748 -- Email: speyer@asu.edu
%
%\item \textbf{Dan Stanzione} \\
%Deputy Director, Texas Advanced Computing Center, The University of Texas at Austin \\
%Phone: (512) 475-9411 -- Email: dan@tacc.utexas.edu

%\end{itemize}

\end{document}
