\documentclass[11pt,letterpaper]{letter}
\usepackage{latexsym}
%\usepackage{times}
\usepackage[letterpaper,left=1.0in,top=0.2in,right=1.0in,bottom=1.0in,includehead]{geometry}
%\usepackage[letterpaper,left=0.75in,top=0.75in,right=0.75in,bottom=0.75in,includehead]{geometry}
\signature{Anthony DiGirolamo}           % name for signature
\longindentation=0pt                     % needed to get closing flush left
\let\raggedleft\raggedright              % needed to get date flush left
\begin{document}

\begin{letter}{
Software Support Specialist \\
Reference Code: NB50271401\\
National Center for Computational Sciences\\
Oak Ridge National Laboratory
}

\begin{flushleft}
{\Large\bf Anthony DiGirolamo}\\
{\small 6815 S McClintock Dr APT 2262, Tempe, AZ 85283 -- Phone: (602) 710-0457 -- E-mail: anthony.d@asu.edu}
\vskip 1.5pt
\hrule height 0.4pt
\end{flushleft}

\opening{ Dear Hiring Department, }

\noindent Please consider this letter and resume in application for the
``Software Support Specialist'' position, Reference Code NB50271401.

\noindent My name is Anthony DiGirolamo, and I am a staff member of the High
Performance Computing Initiative (HPCI) at Arizona State University (ASU). I
have a Bachelor of Science degree in computer science and over five years
working in the information technology field.
%I believe my X years working would enable me to perform
I have attached a resume highlighting my professional and academic experiences.

% \noindent I was introduced to High Performance Computing (HPC) during my
% undergraduate coursework and my interest continues today. My research has
% focused on parallel debugging, and I have contributed two publications to the
% field. This work resulted in a prototype debugger that I tested on user codes
% at ASU and exposed hard to find errors that only manifest themselves when
% running on a large number of cores. I am also familiar with Cloud Computing. I
% can develop applications using Hadoop, HBase, and the Map/Reduce framework to
% process large amounts of data in a scalable manner.

\noindent As a member of the HPCI operations team at ASU I tackle problems
regarding system usage, application debugging, and tool development. I assist
with software and hardware installation, maintenance, testing, and
documentation. Additionally, I teach tutorial classes on programming with C,
Fortran, and the Message Passing Interface (MPI) to our users.  The majority of
my work involves the installation of software packages. I handle installing
compilers, libraries, and other applications our users request. Many libraries
and applications usually need to be compiled multiple times with different
compilers. As such, the list of packages I maintain grows very quickly. In many
cases, I must hand tune compiler flags and configure files to ensure an
application builds correctly and against the libraries we require. Once a piece
of software is ready for the user, I often work with them directly to ensure it
is performing well.

%\noindent I am also interested in web application development, and I have
%worked on web-based projects at ASU. I have a clear understanding of how to
%meet the needs of a customer and deliver a solution using an agile
%approach. I have a strong background in computer science including
%information assurance and relational database courses. Using these skills,
%I produced a web-based document management system that provided storage,
%sharing, and user management with a heavy focus on security. Furthermore, I
%am skilled with Ruby on Rails, and I am experienced with deployment in a
%production environment, security concerns, and unit/functional testing.

\noindent Thank you for taking the time to consider my application.
I am available to discuss this opportunity and answer any questions at your convenience.
I can be contacted over email at anthony.d@asu.edu or by phone at (602) 710-0457.

\closing{Sincerely,}

\vfill
\end{letter}

\end{document}
