\documentclass[12pt,letterpaper]{article}
\usepackage{latexsym}
%\usepackage{times}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{lastpage}
\usepackage[hidelinks]{hyperref}

\usepackage[letterpaper,left=0.5in,top=0.5in,right=0.5in,bottom=0.5in,includehead]{geometry}

\hypersetup{
	pdfauthor={Mark Keele},
	pdftitle={Resume},
}

\fancyhf{}
\headwidth 7.0truein
\setlength{\headheight}{16.35002pt}
\lhead{{\Large \textbf{Mark Keele}}}
\rhead{\href{http://keele.me}{keele.me} -- \
(931) 434-9560 -- \
\href{mailto:m.keele88@gmail.com}{m.keele88@gmail.com}}

\author{Mark Keele}
\title{Resume}
\date{\today}
\begin{document}


\subsection*{Objective}
To secure an internship position for the Summer of 2015 with a concentration
in Web Development, Networking, and Security where I can continue to
work towards my goal of being proficient in the full stack of Web Development.

\subsection*{Profile}

\begin{itemize}

  \item Web applications developer with 4 years of experience

  \item Experience with multiple Model View Controller frameworks

  \item Comfortable actualizing projects from conception to deployment

  \item Ability to communicate with clients and understand requirements

\end{itemize}

\subsection*{Technical Skills}

\begin{itemize}

  \item Real-time application development using all Javascript stack including
  NodeJS RESTful APIs and Sockets, MongoDB storage, and AngularJS front-end
  interface

  \item MVC web application development with Ruby on Rails, JavaScript, CSS, and
  MySQL including production level deployment with Linux and Apache

  \item Unix based systems experience including shell scripting, process management,
  server deployment, and application hosting

  \item Pragmatic developer accustomed to collaborative workflow,
  agile project management, and version control software such as Git

  \item Hardware level experience with embedded systems and C

\end{itemize}

\subsection*{Education}

\begin{itemize}
	\item \textbf{Master of Science in Computer Science -- Graduation 05/2016}
	\hfill{GPA: 4.0} \\
	School of Informatics and Computing, Indiana University -- Bloomington, Indiana

	\item \textbf{Bachelor of Science in Computer Science -- Completed 12/2012}
	\hfill{GPA: 3.0 }\\
	College of Basic and Applied Sciences, Middle Tennessee State University -- Murfreesboro, Tennessee
\end{itemize}


\subsection*{Work Experience}

\begin{itemize}

\item \textbf{Research Assistant, Center for Research in Extreme Scale Technologies}
\hfill{08/2013 -- Present} \\
Indiana University -- Bloomington, Indiana

\begin{itemize}

  \item Developed and deployed both a client side and server side web
  application that is used as a part of the GENI Network test bed.

  \item The client side application provides real-time updates, using Web Sockets,
  on the elements of a user's network topology. Users could submit measurement
  tests and view the results.

  \item The server side application exposed a secure RESTful HTTP and
  Socket API that users could query directly for their data.

  \item Project exists as a layer in an existing network instrumentation and
  measurement system. Communicates with a central application that represents
  network topologies. Experiment data could be stored and measurement objects
  could be created.

  \item Gave conference talk on the functionality and capabilities of the software.
  Made available for attendees to experiment with.

\end{itemize}


\item \textbf{Intern - Ruby on Rails Developer, Leadership Computing}
\hfill{06/2012 -- 07/2013} \\
Oak Ridge National Laboratory -- Oak Ridge, Tennessee

\begin{itemize}

	\item Designed, developed, tested, and deployed a web application using the Ruby
	on Rails framework. Application used internally to track resources and allocations
  of users and projects for the Supercomputers.

  \item Closely collaborated with mentor, database designer, system administrator, and end users.
  Striking a balance between technical requirements and end user workflow was critical.

  \item Engaged in Test Driven Development methodologies in a pair-programming environment
  with an emphasis on continuous refactoring.
  Regression testing using both scenario tests with Cucumber and unit tests with RSpec.

\end{itemize}


%\item \textbf{Lab Assistant, Business and Aerospace Lab}
%\hfill{05/2008 -- 05/2012} \\
%Middle Tennessee State University -- Murfreesboro, Tennessee
%
%\begin{itemize}
%
%  \item Assisted a high volume of students and faculty at the most visited
%  computer laboratory on campus.
%
%  \item Mastered all computer software and hardware available in the laboratory.
%  Software included Office Suite, Visual Studio, and AutoCAD. Hardware included
%  printers, scanners, projectors, touchscreens, and computers.
%
%\end{itemize}

%\item \textbf{Work Student Student, Computer Science Department}
%\hfill{08/2007 -- 05/2008} \\
%Middle Tennessee State University -- Murfreesboro, Tennessee

%\begin{itemize}

%	\item ...

%	\item ...

%\end{itemize}

%\pagebreak

%\item \textbf{Camera Operator, Peahead Productions}
%\hfill{08/2003 -- 08/2007} \\
%Channel 6 Studio -- Tullahoma, Tennessee

%\begin{itemize}

%	\item ...

%	\item ...

%\end{itemize}

\end{itemize}

\subsection*{Projects}

\begin{itemize}
  \item \textbf{XINU OS on Raspberry Pi}
  \begin{itemize}

    \item Wrote basic operating system commands and added synchronization support using semaphores.

    \item Included notion of futures and promises so that processes could synchronize on a given computation.

  \end{itemize}

  \item \textbf{Lux Ex Machina}
  \begin{itemize}

    \item An embedded system acting as a light meter that recommends shutter speed,
    aperture, and ISO to the user. Accomplished using ARM board, light sensor, and
    Wi-Fi adapter.

    \item Front-end web application used to receive data, make calculations, and
    respond to device dimensions. Experience was tailored for iPhone and Android smartphones.

  \end{itemize}

  \item \textbf{Summer of Networking}
  \begin{itemize}

    \item Study based around practical aspects of networking from the OSI model.
    Focused on data link layer, network layer, and transport layer.

    \item Concentrated on finding vulnerabilities in the web browser certificate system.
    Generation of wildcat certificates was used to capture login credentials during a Man in the Middle Attack.

  \end{itemize}

  \item \textbf{SCinet Student Volunteer}
  \begin{itemize}

    \item World's fastest network created due to collaborated with several other volunteers.
    Laid and tested fiber connections between booths and network operations centers.

    \item Developed on Danjo based Intranet used to manage the services of SCinet.
    Answered tickets and fixed issues as they arose.

  \end{itemize}

\end{itemize}

\end{document}
